module2_eco_pol_factors

### 2023-09-20 module2/module2IVgraphs.Rmd
lot of changes because I wasn't opening the project file.

demorisk2 <- codedmodule2%>%
  group_by(SYSTEMDEMO)%>%
  filter(SYSTEMDEMO %in% c(1, 5))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  select(SYSTEMDEMO, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(SYSTEMDEMO)

>>>>

demorisk2 <- codedmodule2%>%
  group_by(SYSTEMDEMO)%>%
  filter(SYSTEMDEMO %in% c(1,5))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  select(SYSTEMDEMO, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(SYSTEMDEMO)

### 2023-09-20 module2/module2extra.Rmd
lot of changes because I wasn't opening the project file.

>>>>

Factor Analysis on the economic and political values scale: 4 factor spaces

```{r, echo=FALSE}
#factor analysis with 4 factor spaces

ecopolscale4.fa <- fa(ecopolscalescores, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
print.psych(ecopolscale4.fa, cut = 0.3, sort = TRUE)
fa.diagram(ecopolscale4.fa)

loadingsecopol4 <- unclass(ecopolscale4.fa$loadings)

loadingstableecopol4 <- cbind(loadingsecopol4)

faecopol4 <- as_tibble(loadingstableecopol4) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(faecopol4, digits= 2)

Varexplecopol4 <- unclass(ecopolscale4.fa$Vaccounted)

knitr::kable(Varexplecopol4, digits = 2)

Factor Analysis on the economic and political values scale: 6 factor spaces

ecopolscale3.fa <- fa(ecopolscalescores, nfactors=3, scores=TRUE, rotate="varimax", fm="pa")
print.psych(ecopolscale3.fa, cut = 0.3, sort = TRUE)
fa.diagram(ecopolscale3.fa)

loadingsecopol3 <- unclass(ecopolscale3.fa$loadings)

loadingstableecopol3 <- cbind(loadingsecopol3)

faecopol3 <- as_tibble(loadingstableecopol3) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2, PA3) %>%
  arrange(desc(PA1))

knitr::kable(faecopol3, digits= 2)

Varexplecopol3 <- unclass(ecopolscale3.fa$Vaccounted)

knitr::kable(Varexplecopol3, digits = 2)
```

#factor analysis with 2, 4 and 6 factor spaces

ecopolscale.fa <- fa(ecopolscalescores, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
print.psych(ecopolscale.fa, cut = 0.3, sort = TRUE)
fa.diagram(ecopolscale.fa)

# Calculate eigenvalues
ecopol.eigenvalues <- ecopolscale.fa$values

loadingsecopol <- unclass(ecopolscale.fa$loadings)

loadingstableecopol <- cbind(loadingsecopol)

twofaecopol <- as_tibble(loadingstableecopol) %>%
add_column("Items" = c("Local politicians shouldn't have to ask permission from the central government to implement policies",
 "Laws and policies would be implemented more smoothly if more power lay with the central government",
"It is good to have a strong leader who does not have to bother with elections", 
 "Experts, not the government, should make decisions according to what they think is best for the country" , 
"It is very important to have a democratic political system because it ensures that no individual leader has too much power" , 
"There should be a system governed by religious law" , 
"Large corporations are destroying the local industries in India and benefiting only a handful of people" , 
"Large scale industries are required for the development of the country that will benefit everyone" , 
"India would be better off if foreign companies didn't come to here" , 
"Foreign companies have led to a range of benefits for the Indian people and society", 
"Economic growth and creating jobs should be prioritized over environmental protection" , 
"Polluting industries that spoil the environment should be shut down even if it costs people their jobs", 
"All businesses and industries should be owned privately", 
"The government should own most large businesses and industries", 
"Regardless of ownership, the government should pass strong regulations and implement them", 
"There is too much red-tape and the government should not interfere with businesses and industries" , 
"A limit should be put to how much wealth a person can amass",
 "Rapid mechanization of work is taking away jobs from workers in this country"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(twofaecopol, digits= 2)

Varexplecopol <- unclass(ecopolscale.fa$Vaccounted)

knitr::kable(Varexplecopol, digits = 2)

**Economic and Political characteristics of the energy technology scale -  Solar Energy and rooftop solar energy**

Cronbach's alpha test on the Eco-Pol characteristics of the technology -  Solar Energy

#alpha test on Eco-pol characteristics of the technology

Solar <- codedmodule2 %>%
dplyr::select("DISPLACESOLAR":"RELYSOLAR") %>%
dplyr::rename("Solar energy is leading to displacement of people from their land" = "DISPLACESOLAR") %>%
dplyr::rename("Solar energy increases pollution of air/water/land" = "POLLUTESOLAR")%>%
dplyr::rename("Solar energy poses a great risk to the health of people living around it" = "HEALTHSOLAR")%>%
dplyr::rename("Solar energy will bring jobs to the local community" = "JOBSSOLAR")%>%
dplyr::rename("Solar energy spoils the natural beauty of the landscape" = "BEAUTYSOLAR")%>%
dplyr::rename("I would be proud if my community used solar energy" = "PRIDESOLAR")%>%
dplyr::rename("Solar energy is a mark of pride for our nation" = "NPRIDESOLAR") %>%
dplyr::rename("Solar energy pushes forward the country's development" = "DEVSOLAR")%>%
dplyr::rename("Solar energy brings economic prosperity to the surrounding regions" = "PROSPERSOLAR")%>%
dplyr::rename("I don't like the idea that I have to rely on the government for electricity from (large scale solar energy)" = "RELYSOLAR")%>%
  na.omit()

psych::alpha(Solar, check.keys = TRUE)

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 2 factor spaces

#factor analysis with 2 factor spaces

solar.fa <- fa(Solar, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar <- unclass(solar.fa$loadings)

loadingstablesolar <- cbind(loadingssolar)

fasolar <- as_tibble(loadingstablesolar) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2)%>%
arrange(desc(PA1))

knitr::kable(fasolar, digits= 2)

Varexplsolar <- unclass(solar.fa$Vaccounted)

knitr::kable(Varexplsolar, digits = 2)
```

Factor Analysis on the eco- pol characteristics of the technology, Solar Energy : 4 factor spaces

#factor analysis with  4 a factor spaces

solar4.fa <- fa(Solar, nfactors=4, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(solar.fa, cut = 0.4, sort = TRUE)
#fa.diagram(solar.fa)

loadingssolar4 <- unclass(solar4.fa$loadings)

loadingstablesolar4 <- cbind(loadingssolar4)

fasolar4 <- as_tibble(loadingstablesolar4) %>%
add_column("Items" = c("Solar energy is leading to displacement of people from their land",
"Solar energy increases pollution of air/water/land",
"Solar energy poses a great risk to the health of people living around it",
"Solar energy will bring jobs to the local community",
"Solar energy spoils the natural beauty of the landscape",
"I would be proud if my community used solar energy",
"Solar energy is a mark of pride for our nation",
"Solar energy pushes forward the country's development",
"Solar energy brings economic prosperity to the surrounding regions",
"I don't like the idea that I have to rely on the government for electricity from (large scale) solar energy"))%>%
dplyr::select("Items",PA1, PA2, PA3, PA4) %>%
  arrange(desc(PA1))

knitr::kable(fasolar4, digits= 2)

Varexplsolar4 <- unclass(solar4.fa$Vaccounted)

knitr::kable(Varexplsolar4, digits = 2)
```

```{r, echo=FALSE}
ROOFS<- codedmodule2 %>%
 dplyr::select("DISPLACEROOFS":"RELYROOFS")

psych::alpha(ROOFS, check.keys = TRUE)

```{r, echo=FALSE}
#factor analysis with 2, 4 and 6 factor spaces

roofs.fa <- fa(ROOFS, nfactors=2, scores=TRUE, rotate="varimax", fm="pa")
#print.psych(roofs.fa, cut = 0.4, sort = TRUE)
#fa.diagram(roofs.fa)

loadingsroofs <- unclass(roofs.fa$loadings)

loadingstableroofs <- cbind(loadingsroofs)

faroofs <- as_tibble(loadingstableroofs) %>%
add_column("Items" = c("Rooftop solar is leading to displacement of people from their land",
"Rooftop solar increases pollution of air/water/land", 
"Rooftop solar poses a great risk to the health of people living around it",
"Rooftop solar will bring jobs to the local community",
"Rooftop solar spoils the natural beauty of the landscape" , 
"I would be proud if my community used Rooftop solar" , 
"Rooftop solar is a mark of pride for our nation", 
"Rooftop solar pushes forward the country's development" , 
"Rooftop solar brings economic prosperity to the surrounding regions" , 
"I don't like the idea that I have to rely on the government for electricity from (large scale) Rooftop solar")) %>%
dplyr::select("Items",  PA1, PA2)%>%
  arrange(desc(PA1))

knitr::kable(faroofs, digits = 2)

Varexplroofs <- unclass(roofs.fa$Vaccounted)

knitr::kable(Varexplroofs, digits = 2)

### 2023-09-20 module2/moduletwoanalysis.Rmd
conducting the Kruskal wallis test on DVs
lot of changes because I wasn't opening the project file.

bar plots for median of perceived risk and benefit from various energy technologies

@@

ecopolscalepca <- ecopolscalescores %>%
  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
  prcomp(center = TRUE,scale. = TRUE)

>>>>

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q4: How do perception of risk and perception of benefit compare with each other?

# what is this comparison telling us ?

# summary statistics for risks from different energy sources
library(tidyverse)

# Filter variables of interest
joineddf_subset <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  select(starts_with("Risky"), 
         starts_with("Ben"))

str(joineddf_subset)

# Melt the data frame to long format
long_format <- joineddf_subset %>% 
  pivot_longer(everything(), names_to = "technology", values_to = "value") %>%
  mutate(risk_or_benefit = if_else(str_detect(technology, "Risky"), "risk", "benefit"),
         technology = str_replace(technology, "Risky_|Ben_", ""))

# Calculate mean and sd for each technology and category (risk or benefit)
summary_df <- long_format %>%
  group_by(technology, risk_or_benefit) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE),
            se = sd(value, na.rm = TRUE) / sqrt(n()),
            .groups = "drop")

# Order technologies by mean risk
order_risk <- summary_df %>% 
  filter(risk_or_benefit == "risk") %>%
  arrange(mean) %>% 
  pull(technology)

# Change the levels of factor 'technology'
summary_df$technology <- factor(summary_df$technology, levels = order_risk)

# Plotting the data
ggplot(summary_df, aes(x = technology, y = mean, fill = risk_or_benefit)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = 0.3, position = position_dodge(0.9)) +
  ylim(0, 5) +
  scale_fill_manual("legend", 
                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
  labs(y = "Mean Values", x = "Energy Technologies", fill = "Perceived") +
  ggtitle("Perceived risk and benefit from centrally managed energy technologies") +
  coord_flip()

# add a star in front of all bars to show these differences are significant at 0.05 
# error bars represent

```
bar plots for median of perceived risk and benefit from various energy technologies

@@

ecopolscalepca <- ecopolscalescores %>%
  select(!starts_with(c("Risky","Gender","Caste","Religion","State")))%>%
  prcomp(center = TRUE, scale. = TRUE)
